\textbf{ Spectrophotometric parallaxes with \project{The Cygnet}:\\ Accurate distances for luminous red-giant stars }

### 2018-08-03 paper/sp.tex
figure

We optimize two models, one for Training Set A and one for Training Set B.
The two models are applied to the two splits of the Parent Sample, Parent Sample
A and Parent Sample B, using the A-trained model on Parent Sample B and
\foreign{vice versa}.
For the purposes of assessing the accuracy and precision of the model, this
train-and-test framework constitutes a two-fold cross-validation.
Results of this cross-validation is shown in HOGG WHAT FIGURE.
For the stars with highest \gaia-measured parallax signal-to-noise,
the spectrophotometric model is predicting the \gaia\ parallaxes with little bias
and a scatter of better than 9~percent.

>>>>

We optimize two models, one for Training Set A and one for Training Set B.
The two models are applied to the two splits of the Parent Sample, Parent Sample
A and Parent Sample B, using the A-trained model on Parent Sample B and
\foreign{vice versa}.
For the purposes of assessing the accuracy and precision of the model, this
train-and-test framework constitutes a two-fold cross-validation.
Results of this cross-validation is shown in \figurename~\ref{fig:xval}.
For the stars with highest \gaia-measured parallax signal-to-noise,
the spectrophotometric model is predicting the \gaia\ parallaxes with little bias
and a scatter of better than 9~percent.
\begin{figure}
\caption{The predictive accuracy of the model, in the two-fold cross-validation.
  Each panel shows \gaia\ astrometric parallaxes $\gparallax_n$ on the vertical axis
  and our spectrophotometric parallaxes $\sparallax$ on the horizontal axis.
  The left panel shows the full Parent Sample, the middle panel shows the Training Set
  stars (which pass \gaia\ quality checks; see text), and the right panel shows a
  subset of stars with very high astrometric parallax signal-to-noise. This latter
  set plays no particular role in the method, but it can be used to demonstrate or
  assess the prediction precision. Fractional precision of the prediction
  is XXXX HOGG MEASURED HOW?\label{fig:xval}}
\end{figure}
